PANCHANGE_analysis

### 2020-11-20 PANCHANGE_analysis.Rmd
tweaked figure height and width for violin plots

```{r gad.sum violin plot Sample, fig.height=3.5, fig.width=2.5}
dat.long.gad.sum %>%
  mutate(Time_point_renamed = fct_recode(Time_point, 
            "Prepandemic" = "prepan",
            "Retrospective" = "retro",
            "Baseline" = "base")
         ) %>%
         mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
            "Baseline",
            "Retrospective",
            "Prepandemic")
         ) %>%
  ggplot(mapping = aes(
    x = Time_point_reordered,
    y = gad.sum_score,
    fill = Time_point_reordered)) +
  geom_hline(yintercept = 5, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    trim = FALSE,
    alpha = 0.5
    ) +
  geom_point(
    aes(
      y = gad.sum_score,
      color = Time_point_reordered),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8) +
#  geom_boxplot(
#    width = .1,
#    guides = FALSE,
#    outlier.shape = NA,
#    alpha = 0.5) +
 stat_summary(fun.y = mean,
              fun.ymin = function(x) mean(x) - sd(x), 
              fun.ymax = function(x) mean(x) + sd(x), 
              geom = "pointrange"
              ) +
  labs(
    y = "GAD7 scores",
    fill = "Time point") +
  theme_personal +
  theme(
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
  scale_alpha(guide = 'none') +
  scale_size(guide = 'none') +
  scale_color_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline"),
    guide = "none") +
  facet_wrap(facets = vars(Sample),
             nrow = 4
             ) +
  coord_flip()
```

```{r gad.sum violin plot Disorder_hierarchical}
dat.long.gad.sum %>%
  mutate(Time_point_renamed = fct_recode(Time_point, 
            "Prepandemic" = "prepan",
            "Retrospective" = "retro",
            "Baseline" = "base")
         ) %>%
         mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
            "Baseline",
            "Retrospective",
            "Prepandemic")
         ) %>%
  ggplot(mapping = aes(
    x = Time_point_reordered,
    y = gad.sum_score,
    fill = Time_point_reordered)) +
  geom_hline(yintercept = 5, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    trim = FALSE,
    alpha = 0.5
    ) +
  geom_point(
    aes(
      y = gad.sum_score,
      color = Time_point_reordered),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8) +
#  geom_boxplot(
#    width = .1,
#    guides = FALSE,
#    outlier.shape = NA,
#    alpha = 0.5) +
 stat_summary(fun.y = mean,
              fun.ymin = function(x) mean(x) - sd(x), 
              fun.ymax = function(x) mean(x) + sd(x), 
              geom = "pointrange"
              ) +
  labs(
    y = "GAD7 scores",
    fill = "Time point") +
  theme_personal +
  theme(
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
  scale_alpha(guide = 'none') +
  scale_size(guide = 'none') +
  scale_color_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline"),
    guide = "none") +
  facet_wrap(facets = vars(Disorder_hierarchical)
             ) +
  coord_flip()
```

@@

```{r phq.sum violin plot Sample, fig.height=3.5, fig.width=2.5}
dat.long.phq.sum %>%
  mutate(Time_point_renamed = fct_recode(Time_point, 
                                         "Prepandemic" = "prepan",
                                         "Retrospective" = "retro",
                                         "Baseline" = "base")
  ) %>%
  mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
                                            "Baseline",
                                            "Retrospective",
                                            "Prepandemic")
  ) %>%
  ggplot(mapping = aes(
    x = Time_point_reordered,
    y = phq.sum_score,
    fill = Time_point_reordered)) +
  geom_hline(yintercept = 8, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 11, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    trim = FALSE,
    alpha = 0.5
  ) +
  geom_point(
    aes(
      y = phq.sum_score,
      color = Time_point_reordered),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8) +
  #  geom_boxplot(
  #    width = .1,
  #    guides = FALSE,
  #    outlier.shape = NA,
  #    alpha = 0.5) +
  stat_summary(fun.y = mean,
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "pointrange"
  ) +
  labs(
    y = "PHQ9 scores",
    fill = "Time point") +
  theme_personal +
  theme(
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
  scale_alpha(guide = 'none') +
  scale_size(guide = 'none') +
  scale_color_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline"),
    guide = "none") +
  facet_wrap(facets = vars(Sample),
             nrow = 4
  ) +
  coord_flip()
```

```{r phq.sum violin plot Disorder_hierarchical}
dat.long.phq.sum %>%
  mutate(Time_point_renamed = fct_recode(Time_point, 
                                         "Prepandemic" = "prepan",
                                         "Retrospective" = "retro",
                                         "Baseline" = "base")
  ) %>%
  mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
                                            "Baseline",
                                            "Retrospective",
                                            "Prepandemic")
  ) %>%
  ggplot(mapping = aes(
    x = Time_point_reordered,
    y = phq.sum_score,
    fill = Time_point_reordered)) +
  geom_hline(yintercept = 8, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 11, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    trim = FALSE,
    alpha = 0.5
  ) +
  geom_point(
    aes(
      y = phq.sum_score,
      color = Time_point_reordered),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8) +
  #  geom_boxplot(
  #    width = .1,
  #    guides = FALSE,
  #    outlier.shape = NA,
  #    alpha = 0.5) +
  stat_summary(fun.y = mean,
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "pointrange"
  ) +
  labs(
    y = "PHQ9 scores",
    fill = "Time point") +
  theme_personal +
  theme(
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
  scale_alpha(guide = 'none') +
  scale_size(guide = 'none') +
  scale_color_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline"),
    guide = "none") +
  facet_wrap(facets = vars(Disorder_hierarchical)
  ) +
  coord_flip()
```

@@

```{r ocir.sum violin plot Sample, fig.height=3.5, fig.width=2.5}
dat.long.ocir.sum %>%
  mutate(Time_point_renamed = fct_recode(Time_point, 
                                         "Prepandemic" = "prepan",
                                         "Retrospective" = "retro",
                                         "Baseline" = "base")
  ) %>%
  mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
                                            "Baseline",
                                            "Retrospective",
                                            "Prepandemic")
  ) %>%
  ggplot(mapping = aes(
    x = Time_point_reordered,
    y = ocir.sum_score,
    fill = Time_point_reordered)) +
  geom_hline(yintercept = 21, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    trim = FALSE,
    alpha = 0.5
  ) +
  geom_point(
    aes(
      y = ocir.sum_score,
      color = Time_point_reordered),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8) +
  #  geom_boxplot(
  #    width = .1,
  #    guides = FALSE,
  #    outlier.shape = NA,
  #    alpha = 0.5) +
  stat_summary(fun.y = mean,
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "pointrange"
  ) +
  labs(
    y = "OCI-R scores",
    fill = "Time point") +
  theme_personal +
  theme(
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
  scale_alpha(guide = 'none') +
  scale_size(guide = 'none') +
  scale_color_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline"),
    guide = "none") +
  facet_wrap(facets = vars(Sample),
             nrow = 4
  ) +
  coord_flip()
```

```{r ocir.sum violin plot Disorder_hierarchical}
dat.long.ocir.sum %>%
  mutate(Time_point_renamed = fct_recode(Time_point, 
                                         "Prepandemic" = "prepan",
                                         "Retrospective" = "retro",
                                         "Baseline" = "base")
  ) %>%
  mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
                                            "Baseline",
                                            "Retrospective",
                                            "Prepandemic")
  ) %>%
  ggplot(mapping = aes(
    x = Time_point_reordered,
    y = ocir.sum_score,
    fill = Time_point_reordered)) +
  geom_hline(yintercept = 21, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    trim = FALSE,
    alpha = 0.5
  ) +
  geom_point(
    aes(
      y = ocir.sum_score,
      color = Time_point_reordered),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8) +
  #  geom_boxplot(
  #    width = .1,
  #    guides = FALSE,
  #    outlier.shape = NA,
  #    alpha = 0.5) +
  stat_summary(fun.y = mean,
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "pointrange"
  ) +
  labs(
    y = "OCI-R scores",
    fill = "Time point") +
  theme_personal +
  theme(
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
  scale_alpha(guide = 'none') +
  scale_size(guide = 'none') +
  scale_color_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline"),
    guide = "none") +
  facet_wrap(facets = vars(Disorder_hierarchical)
  ) +
  coord_flip()
```

>>>>

```{r gad.sum violin plot Sample, fig.height=14, fig.width=8}
dat.long.gad.sum %>%
  mutate(Time_point_renamed = fct_recode(Time_point, 
            "Prepandemic" = "prepan",
            "Retrospective" = "retro",
            "Baseline" = "base")
         ) %>%
         mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
            "Baseline",
            "Retrospective",
            "Prepandemic")
         ) %>%
  ggplot(mapping = aes(
    x = Time_point_reordered,
    y = gad.sum_score,
    fill = Time_point_reordered)) +
  geom_hline(yintercept = 5, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    trim = FALSE,
    alpha = 0.5
    ) +
  geom_point(
    aes(
      y = gad.sum_score,
      color = Time_point_reordered),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8) +
#  geom_boxplot(
#    width = .1,
#    guides = FALSE,
#    outlier.shape = NA,
#    alpha = 0.5) +
 stat_summary(fun.y = mean,
              fun.ymin = function(x) mean(x) - sd(x), 
              fun.ymax = function(x) mean(x) + sd(x), 
              geom = "pointrange"
              ) +
  labs(
    y = "GAD7 scores",
    fill = "Time point") +
  theme_personal +
  theme(
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
  scale_alpha(guide = 'none') +
  scale_size(guide = 'none') +
  scale_color_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline"),
    guide = "none") +
  facet_wrap(facets = vars(Sample),
             nrow = 4
             ) +
  coord_flip()

```{r gad.sum violin plot Disorder_hierarchical, fig.height=10, fig.width=15}
dat.long.gad.sum %>%
  mutate(Time_point_renamed = fct_recode(Time_point, 
            "Prepandemic" = "prepan",
            "Retrospective" = "retro",
            "Baseline" = "base")
         ) %>%
         mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
            "Baseline",
            "Retrospective",
            "Prepandemic")
         ) %>%
  ggplot(mapping = aes(
    x = Time_point_reordered,
    y = gad.sum_score,
    fill = Time_point_reordered)) +
  geom_hline(yintercept = 5, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    trim = FALSE,
    alpha = 0.5
    ) +
  geom_point(
    aes(
      y = gad.sum_score,
      color = Time_point_reordered),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8) +
#  geom_boxplot(
#    width = .1,
#    guides = FALSE,
#    outlier.shape = NA,
#    alpha = 0.5) +
 stat_summary(fun.y = mean,
              fun.ymin = function(x) mean(x) - sd(x), 
              fun.ymax = function(x) mean(x) + sd(x), 
              geom = "pointrange"
              ) +
  labs(
    y = "GAD7 scores",
    fill = "Time point") +
  theme_personal +
  theme(
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
  scale_alpha(guide = 'none') +
  scale_size(guide = 'none') +
  scale_color_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline"),
    guide = "none") +
  facet_wrap(facets = vars(Disorder_hierarchical)
             ) +
  coord_flip()
```

@@

```{r phq.sum violin plot Sample, fig.height=14, fig.width=8}
dat.long.phq.sum %>%
  mutate(Time_point_renamed = fct_recode(Time_point, 
                                         "Prepandemic" = "prepan",
                                         "Retrospective" = "retro",
                                         "Baseline" = "base")
  ) %>%
  mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
                                            "Baseline",
                                            "Retrospective",
                                            "Prepandemic")
  ) %>%
  ggplot(mapping = aes(
    x = Time_point_reordered,
    y = phq.sum_score,
    fill = Time_point_reordered)) +
  geom_hline(yintercept = 8, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 11, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    trim = FALSE,
    alpha = 0.5
  ) +
  geom_point(
    aes(
      y = phq.sum_score,
      color = Time_point_reordered),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8) +
  #  geom_boxplot(
  #    width = .1,
  #    guides = FALSE,
  #    outlier.shape = NA,
  #    alpha = 0.5) +
  stat_summary(fun.y = mean,
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "pointrange"
  ) +
  labs(
    y = "PHQ9 scores",
    fill = "Time point") +
  theme_personal +
  theme(
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
  scale_alpha(guide = 'none') +
  scale_size(guide = 'none') +
  scale_color_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline"),
    guide = "none") +
  facet_wrap(facets = vars(Sample),
             nrow = 4
  ) +
  coord_flip()
```

```{r phq.sum violin plot Disorder_hierarchical, fig.height=10, fig.width=15}
dat.long.phq.sum %>%
  mutate(Time_point_renamed = fct_recode(Time_point, 
                                         "Prepandemic" = "prepan",
                                         "Retrospective" = "retro",
                                         "Baseline" = "base")
  ) %>%
  mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
                                            "Baseline",
                                            "Retrospective",
                                            "Prepandemic")
  ) %>%
  ggplot(mapping = aes(
    x = Time_point_reordered,
    y = phq.sum_score,
    fill = Time_point_reordered)) +
  geom_hline(yintercept = 8, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 11, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    trim = FALSE,
    alpha = 0.5
  ) +
  geom_point(
    aes(
      y = phq.sum_score,
      color = Time_point_reordered),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8) +
  #  geom_boxplot(
  #    width = .1,
  #    guides = FALSE,
  #    outlier.shape = NA,
  #    alpha = 0.5) +
  stat_summary(fun.y = mean,
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "pointrange"
  ) +
  labs(
    y = "PHQ9 scores",
    fill = "Time point") +
  theme_personal +
  theme(
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
  scale_alpha(guide = 'none') +
  scale_size(guide = 'none') +
  scale_color_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline"),
    guide = "none") +
  facet_wrap(facets = vars(Disorder_hierarchical)
  ) +
  coord_flip()
```

@@

```{r ocir.sum violin plot Sample, fig.height=14, fig.width=8}
dat.long.ocir.sum %>%
  mutate(Time_point_renamed = fct_recode(Time_point, 
                                         "Prepandemic" = "prepan",
                                         "Retrospective" = "retro",
                                         "Baseline" = "base")
  ) %>%
  mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
                                            "Baseline",
                                            "Retrospective",
                                            "Prepandemic")
  ) %>%
  ggplot(mapping = aes(
    x = Time_point_reordered,
    y = ocir.sum_score,
    fill = Time_point_reordered)) +
  geom_hline(yintercept = 21, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    trim = FALSE,
    alpha = 0.5
  ) +
  geom_point(
    aes(
      y = ocir.sum_score,
      color = Time_point_reordered),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8) +
  #  geom_boxplot(
  #    width = .1,
  #    guides = FALSE,
  #    outlier.shape = NA,
  #    alpha = 0.5) +
  stat_summary(fun.y = mean,
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "pointrange"
  ) +
  labs(
    y = "OCI-R scores",
    fill = "Time point") +
  theme_personal +
  theme(
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
  scale_alpha(guide = 'none') +
  scale_size(guide = 'none') +
  scale_color_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline"),
    guide = "none") +
  facet_wrap(facets = vars(Sample),
             nrow = 4
  ) +
  coord_flip()
```

```{r ocir.sum violin plot Disorder_hierarchical, fig.height=10, fig.width=15}
dat.long.ocir.sum %>%
  mutate(Time_point_renamed = fct_recode(Time_point, 
                                         "Prepandemic" = "prepan",
                                         "Retrospective" = "retro",
                                         "Baseline" = "base")
  ) %>%
  mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
                                            "Baseline",
                                            "Retrospective",
                                            "Prepandemic")
  ) %>%
  ggplot(mapping = aes(
    x = Time_point_reordered,
    y = ocir.sum_score,
    fill = Time_point_reordered)) +
  geom_hline(yintercept = 21, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_flat_violin(
    position = position_nudge(x = .2, y = 0),
    trim = FALSE,
    alpha = 0.5
  ) +
  geom_point(
    aes(
      y = ocir.sum_score,
      color = Time_point_reordered),
    position = position_jitter(width = .15),
    size = .5,
    alpha = 0.8) +
  #  geom_boxplot(
  #    width = .1,
  #    guides = FALSE,
  #    outlier.shape = NA,
  #    alpha = 0.5) +
  stat_summary(fun.y = mean,
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "pointrange"
  ) +
  labs(
    y = "OCI-R scores",
    fill = "Time point") +
  theme_personal +
  theme(
    axis.text.y = element_blank()
  ) +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
  scale_alpha(guide = 'none') +
  scale_size(guide = 'none') +
  scale_color_manual(
    values = COPINGpalette3,
    breaks = c("Prepandemic", "Retrospective", "Baseline"),
    guide = "none") +
  facet_wrap(facets = vars(Disorder_hierarchical)
  ) +
  coord_flip()
```
